Interactive Summarization of Relational Tables

### 2014-10-30 TableSummarization/Paper/TableSummarization.tex
Added related work

\begin{abstract}
In this paper, we study the following problem: Given a relational table, find the most `interesting' summary of the table, subject to user-specified constraints. The summary consists of a list of `rules', where a rule is a pattern specifying values occurring in some columns of the table, along with the number of tuples that are covered by the rule. For instance, the rule $(a, b, \star, 1000)$ tell us that there are a $1000$ tuples with value $a$ in the first column and $b$ in the second column. We allow the user to specify what kind of rules to prefer in the summary via a black box weighting function, and to further selectively explore parts of the table. We describe an algorithm for finding the approximately optimal list of rules according to the user-specified weighting function, and a sampling based scheme for dealing with large tables. Finally, we demonstrate the usefulness of our summary by performing experiments on a real dataset.
\end{abstract}

@@

%TODO: Change indentation format. All indentation at start, number of indents equal to depth of rule
\begin{table}
\centering
\begin{tabular}{| l | l | l | l | l |}
\hline Store & Product & State & Count & Weight \\
\hline
$\star$ & $\star$ & $\star$ & $6000$ & $0$ \\ \hline
$\triangleright$ target & bicycles & $\star$ & $200$ & $2$ \\ \hline
$\triangleright$ $\star$ & comforters & Massachusetts & $600$ & $2$ \\ \hline
$\triangleright$ walmart & $\star$ & $\star$ & $1000$ & $1$ \\ \hline
\end{tabular}
\caption{Example of a rule based table summary \label{table:introexample}}
\end{table}

@@

% TODO : Also motivate coverage based scoring over only giving top scoring rules i.e. MCount over Count. 
\stitle{Overview of paper:} 
\squishlist

@@

\item In Section 6, we experimentally evaluate the performance of our algorithms a real dataset.
\squishend

@@

The total score for our list of rules is given by $$\text{Score}(R) = \sum_{r \in R} MCount(r)W(r)$$. Our problem is to choose the rule-list that maximises total score. We use $MCount$ rather than Count to increase coverage of the table. If we had defined total score as $$\sum_{r \in R} \text{Count}(r)W(r)$$, then our optimal rule-list would contain rules that repeatedly refer to the most `summarizable' part of the table. For instance, if $a$ and $b$ were the most common values in columns $A$ and $B$, then the summary could consist of rules $(a, b, \star)$, $(a, \star, \star)$, and $(\star, b, \star)$, which tells us nothing about the part of the table with values other than $a$ and $b$.
%TODO: Write an actual example? To also verify what actually happens.

@@

% TODO: Experiments on m_w. Experiments on Sampling schemes.

@@

\section{Related Work}
%TODO: Repeat what we said in intro about interactive, etc.
There has been work on finding interesting rules in OLAP systems~\cite{Sarawagi:2001:UMA:767141.767148, Sarawagi00user-adaptiveexploration, Sarawagi98discovery-drivenexploration}. The work mainly focuses on finding values that occur more often or less often that expected from a max entropy distribution. The work does not guarantee good coverage of the table, since it rates infrequently occurring sets of values as highly as frequently occurring ones.

@@

@@

% Related Work summary :
% Explanation tables takes lots of papers and talks about them in one go in related work. saying they optimize for different opbjective functions. We can say that as well. We have a unique idea of flexible weighting functions for managing the tradeoff between coverage and specificity. 
% Efficient and Effective... Tableaux

>>>>

\begin{abstract}
In this paper, we study the following problem: Given a relational table, find the most `interesting' summary of the table, subject to user-specified constraints. The summary consists of a list of `rules', where a rule is a pattern specifying values occurring in some columns of the table, along with the number of tuples that satisfy that pattern. For instance, the rule $(a, b, \star, 1000)$ tell us that there are a $1000$ tuples with value $a$ in the first column and $b$ in the second column. We allow the user to specify what kind of rules to prefer in the summary via a black box weighting function, and to further selectively explore parts of the table. We describe an algorithm for finding the approximately optimal list of rules according to the user-specified weighting function, and a sampling based scheme for efficiently summarizing large tables. Finally, we demonstrate the usefulness of our summary by performing experiments on a real dataset.
\end{abstract}

@@

\begin{table}
\centering
\begin{tabular}{| l | l | l | l | l |}
\hline Store & Product & State & Count & Weight \\
\hline
$\star$ & $\star$ & $\star$ & $6000$ & $0$ \\ \hline
$\triangleright$ target & bicycles & $\star$ & $200$ & $2$ \\ \hline
$\triangleright$ $\star$ & comforters & Massachusetts & $600$ & $2$ \\ \hline
$\triangleright$ walmart & $\star$ & $\star$ & $1000$ & $1$ \\ \hline
\end{tabular}
\caption{Example of a rule based table summary \label{table:introexample}}
\end{table}

@@

We further discuss related work in Section~\ref{sec:related}.

\stitle{Overview of paper:} 
\squishlist

@@

\item In Section 6, we experimentally evaluate the performance of our algorithms on a real dataset.
\squishend

@@

The total score for our list of rules is given by $$\text{Score}(R) = \sum_{r \in R} MCount(r)W(r)$$. Our problem is to choose the rule-list that maximises total score. We use $MCount$ rather than Count to increase coverage of the table. If we had defined total score as $$\sum_{r \in R} \text{Count}(r)W(r)$$, then our optimal rule-list would contain rules that repeatedly refer to the most `summarizable' part of the table. For instance, if $a$ and $b$ were the most common values in columns $A$ and $B$, then the summary could consist of rules $(a, b, \star)$, $(a, \star, \star)$, and $(\star, b, \star)$, which tells us nothing about the part of the table with values other than $a$ and $b$.

@@

% TODO: Experiments on Sampling schemes.

@@

\section{Related Work}\label{sec:related}
%TODO: Repeat what we said in intro about interactive, etc.
There has been work on finding interesting rules in OLAP systems~\cite{Sarawagi:2001:UMA:767141.767148, Sarawagi00user-adaptiveexploration, Sarawagi98discovery-drivenexploration}. This work, along with other existing work~\cite{Mampaey:2011:TMI:2020408.2020499} focuses on finding values that occur more often or less often that expected from a max entropy distribution. The work does not guarantee good coverage of the table, since it rates infrequently occurring sets of values as highly as frequently occurring ones.

@@

Some related work~\cite{Golab_efficientand, Golab:2008:GNT:1453856.1453900} focuses on finding minimum sized Tableaux that provide improved support and confidence for conditional functional dependencies. There has also been work~\cite{Bu:2005:MSH:1083592.1083644, Lakshmanan:2002:GMA:1287369.1287435, Xiang_succinctsummarization, Geerts04tilingdatabases} on finding hyper-rectangle based covers for tables. All the existing works solve a fixed optimization problem, whereas  we focus on finding an optimal summary for a flexible user-specified weighting function.

@@

% Related Work summary : Is ours the only only that is flexible (due to weight function black box)?
% Explanation tables takes lots of papers and talks about them in one go in related work. saying they optimize for different opbjective functions. We can say that as well. We have a unique idea of flexible weighting functions for managing the tradeoff between coverage and specificity. 
% Succintly summarizing with itemsets-- Mampaey:2011:TMI:2020408.2020499 -- Also seemed to optimize according to max entropy criterion
% Efficient and Effective... Tableaux -- Golab_efficientand -- Similar to conditional functional dep. paper.
% Near Optimal Tableaux Conditional functional dep. -- Golab:2008:GNT:1453856.1453900 -- Finding a smallest sized tableau that provides some confidence and support for a conditional functional dependency.
% MDL Summarization with holes -- Bu:2005:MSH:1083592.1083644 -- Min sized summary with a rectangle and exceptions (holes). 
% Generalized MDL Approach -- Lakshmanan:2002:GMA:1287369.1287435 -- Similar to MDL Approach.
% Overlapped Hyperrectangle -- Xiang_succinctsummarization -- Efficiently find the set of hyperrectangles that covers the data (sets of itemsets)
% Tiling Databases Geerts04tilingdatabases Simlar to hyper-rectangles. Probabilistic interpretation of frequent itemsets.
